Sparse Function Space Representation of Neural Networks for Exploration and Representation

### 2023-04-25 paper/main.tex
updated abstract

\begin{abstract}
Under sequential learning paradigms, such as continual learning (CL) or reinforcement learning (RL), efficient representation and exploration elude standard training techniques for deep learning  models. In RL it is common to receive new information from the environment but due to time and hardware constraints it is not possible to adapt by retraining. Similarly, CL needs  compact representations of previous tasks to avoid forgetting. Recently, methods for converting trained neural networks from weight space to function space show promise in providing a principled approach for probabilistic treatment of the problem. However, they lack ways of sparsifying the representation and methods for quick adaptation to new data. We introduce a sparse representation of the neural network in function space, which enables fast adpatation and compact representation to solve the limitations of the weight space formulation.
\end{abstract}

>>>>

\begin{abstract}
Under sequential learning paradigms, such as Continual Learning (CL) or Reinforcement Learning (RL), deep learning training techniques show shortcomings in retaining previously acquired knowledge and adapting to evolving environments through exploration.
Retraining the model to incorporate new data or avoiding forgetting can be inefficient or impossible in many scenarios, setting hard constraints on time and hardware resources.
Existing techniques for converting trained neural networks from weight to function space allow a principled approach to the problem but still have scaling issues. In this paper, we present a method for sparsifying the representation of the neural networks in function space, which enables fast adaptation and compact representation that solves the limitations of the weight space formulation without the well-known flaws associated with nonparametric models.
\end{abstract}
